### 2019-09-30 website.tex
adds a short section about social media

\subsection{Social Media}

>>>>

\subsection{Social Media} 
Two accounts will be used to monitor and promote social media at the event. The first will be a Twitter account, created specifically for the conference. This account will send out schedules and updates, as well as neat facts about events at the conference. The second account will be a Facebook page which will serve a similar function to the Twitter account. The Facebook page has the added benefit of being able to create events. This ability would be used to provide another source of schedule information to conference attendees.
